# Implementation {#sec-implementation}

## Software

The [cases](https://github.com/maxwestphal/cases) package provides the direct implementation all the multiple comparison procedures under investigation.

The simulation study was conducted with the R package [batchtools](https://CRAN.R-project.org/package=batchtools). 

For generation of the synthetic binary data, the [bindata](https://CRAN.R-project.org/package=bindata) package was used among others.

Version control of employed dependencies is handled via the [renv](https://CRAN.R-project.org/package=renv) package.


## Reproduction

The required packages can be installed/loaded via

```{r, eval=FALSE}
install.packages("renv")
renv::restore()
```

To reproduce the the simulation study two R scripts need to be executed

- R/cases_simstudy_lfc.R,
- R/cases_simstudy_roc.R

In particular for the first run, it is required to setup the directories in the **PREPARATION** section in each file, in particular the **main.dir**.

The simulation (problem, algorithm) parameters are specified as in the main paper. 

## Info

The simulation study has been conducted (originally) with the following system specification.

```{r}
R.Version()
```




